Towards Semantic Patches

### 2010-06-18 papers/MIPS2010/abstract.tex
* SML bib.
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@111 403e655e-980a-47bd-8c60-1ee5348bb6b7

In fact, although dedicated tools exist to formalize the description
of languages and their metatheory (e.g. \textsf{Twelf},
{\cite{pfenning1999system}}), and substantial formalizations have been
undertaken \remtext{TODO citer, mais quoi?}, we still use legacy tools
based on text representation to manage our developments. The general
goal exposed here is to replace this tool chain and make it
language-aware, both on a syntactic side (AST) and on a semantic side
(typing).

>>>>

In fact, although dedicated tools exist to formalize the description
of languages and their metatheory (e.g. \textsf{Twelf},
{\cite{pfenning1999system}}), and substantial formalizations have been
undertaken~[]\cite{lee07}, we still use legacy tools
based on text representation to manage our developments. The general
goal exposed here is to replace this tool chain and make it
language-aware, both on a syntactic side (AST) and on a semantic side
(typing).
